The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
small fix in table 3
Report: Fix weighted score

\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
The \emph{(weighted) score} of a solver in a division of the \maintrack and
\ucoretrack is then defined as the weighted sum of all raw scores $$\sum_{i\in
F} \alpha'_i \cdot \langle e_i \cdot N_i, n_i \cdot N_i, w_i, c_i\rangle$$
where the sum is over all benchmarks in the division to assess parallel
performance, and the weighted sum of all sequential scores to assess sequential
performance.

@@

    Total      & 154238 \gray{(40:60)} & 154424 \gray{(40:60)} & 256973 \gray{(37:46:17)} & 333241 \gray{(33:39:28)}\\

>>>>

\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
The \emph{(weighted) score} of a solver in a division of the \maintrack and
\ucoretrack with $M$ benchmarks is then defined as the weighted sum of all raw
scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N_b, n_b \cdot N_b,
w_b, c_b\rangle$$ where the sum is over all benchmarks in the division to
assess parallel performance, and the weighted sum of all sequential scores to
assess sequential performance.

@@

    Total      & 154238 \gray{(40/60)} & 154424 \gray{(40/60)} & 256973 \gray{(37/46/17)} & 333241 \gray{(33/39/28)}\\
